% NeurIPS 2025 Paper Checklist
% Please Read Instructions printed in the call for papers before completing this checklist.
% Based on earlier NeurIPS checklists.

\section*{Checklist}

% Instructions for Authors:
Please complete this checklist by striking out the parts that do not apply and by answering the questions that do apply.
For example, if your paper does not include theoretical results, strike out phrase "If you are including theoretical results..." and leave the questions unanswered.
Similarly, if your work does not use human subjects, strike out the phrase "If you used crowdsourcing or conducted research with human subjects..." and leave the questions unanswered.

We encourage authors to think critically about the questions and provide thoughtful answers.

N.B. The checklist is part of the NeurIPS submission and needs to be included with the paper. We encourage authors to think critically about the questions and provide thoughtful answers. The submission instructions page on the NeurIPS website has information on how to format the checklist. NeurIPS uses the checklist to promote responsible research practices and to ensure fairness and transparency in the review process.

1.  For all authors...\\
(a) Do the main claims made in the abstract and introduction accurately reflect the paper's contributions and scope? \textcolor{red}{\textbf{TODO: YES/NO/EXPLAIN}}\
(b) Did you describe the limitations of your work? \textcolor{red}{\textbf{TODO: YES/NO/EXPLAIN}}\
(c) Did you discuss any potential negative societal impacts of your work? \textcolor{red}{\textbf{TODO: YES/NO/EXPLAIN}}\
(d) Have you read the ethics review guidelines and ensured that your paper conforms to them? \textcolor{red}{\textbf{TODO: YES/NO/EXPLAIN}}

2.  If you are including theoretical results...\\
(a) Did you state the full set of assumptions of all theoretical results? \textcolor{gray}{\textit{N/A}}\
(b) Did you include complete proofs of all theoretical results? \textcolor{gray}{\textit{N/A}}

3.  If you ran experiments...\\
(a) Did you include the code, data, and instructions needed to reproduce the main experimental results (either in the supplemental material or as a URL)? \textcolor{red}{\textbf{TODO: YES/NO/EXPLAIN}}\
(b) Did you specify all the training details (e.g., data splits, hyperparameters, how they were chosen)? \textcolor{red}{\textbf{TODO: YES/NO/EXPLAIN}}\
(c) Did you report error bars (e.g., with respect to the random seed after running experiments multiple times)? \textcolor{red}{\textbf{TODO: YES/NO/EXPLAIN}}\
(d) Did you include the total amount of compute and the type of resources used (e.g., type of GPUs, internal cluster, or cloud provider)? \textcolor{red}{\textbf{TODO: YES/NO/EXPLAIN}}

4.  If you are using existing assets (e.g., code, data, models) or curating/releasing new assets...\\
(a) If your work uses existing assets, did you cite the creators? \textcolor{red}{\textbf{TODO: YES/NO/EXPLAIN}}\
(b) Did you mention the license of the assets? \textcolor{red}{\textbf{TODO: YES/NO/EXPLAIN}}\
(c) Did you include any new assets either in the supplemental material or as a URL? \textcolor{red}{\textbf{TODO: YES/NO/EXPLAIN}}\
(d) Did you discuss whether and how consent was obtained from people whose data you're using/curating? \textcolor{gray}{\textit{N/A}}\
(e) Did you discuss whether the data you are using/curating contains personally identifiable information or offensive content? \textcolor{gray}{\textit{N/A}}

5.  If you used crowdsourcing or conducted research with human subjects...\\
(a) Did you include the full text of instructions given to participants and screenshots, if applicable? \textcolor{gray}{\textit{N/A}}\
(b) Did you describe any potential participant risks, with links to Institutional Review Board (IRB) approvals, if applicable? \textcolor{gray}{\textit{N/A}}\
(c) Did you include the estimated hourly wage paid to participants and the total amount spent on participant compensation? \textcolor{gray}{\textit{N/A}}